\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-02-01 paper.qmd
Add rsults for PBMC with fixed non-empty bins

error_df <- error_df |>
  mutate(X4 = round(X4/100, 2)) |>
  arrange(X4)

@@

xtable(error_df, caption = "errors for different parameter combinations", label = "tbl-errordiffcomb") |>
  xtable2kable() |>
  kable_styling(latex_options = c("striped", "HOLD_position"), position = "center", full_width = FALSE) |>
  row_spec(0, bold = TRUE) |>
  row_spec(3, bold=T, color = "red")
```

@@

@@

```{r}
#| warning: false
#| echo: false
num_bins_pbmc <- calculate_effective_x_bins(.data = UMAP_pbmc, x = UMAP1,
                                              cell_area = 1) ##23
num_bins_pbmc <- 23

@@

## To find the benchmark value
benchmark_pbmc <- find_benchmark_value(.data = distance_pbmc, distance_col = distance)
#benchmark_pbmc <- 1.035666

@@

>>>>

error_df <- error_df |>
  mutate(X4 = round(X4/100, 2),
         X1 = as.integer(X1)) |>
  arrange(X4)

@@

xtable(error_df, caption = "errors for different parameter combinations", label = "tbl-errordiffcomb") |>
  xtable2kable() |>
  kable_styling(latex_options = c("striped", "HOLD_position"), position = "center", full_width = FALSE) |>
  row_spec(0, bold = TRUE) |>
  row_spec(7, bold=T, color = "red")
```

@@

num_non_empty_bins_pbmc <- df_bin_centroids_pbmc$hexID |> length()

@@

```{r}
#| warning: false
#| echo: false
# num_bins_pbmc <- calculate_effective_x_bins(.data = UMAP_pbmc, x = UMAP1,
#                                               cell_area = 1) ##23

shape_value_pbmc <- calculate_effective_shape_value(.data = UMAP_pbmc,
                                                      x = UMAP1, y = UMAP2) ## 0.8772751

num_bins_pbmc <- find_non_empty_bins(nldr_df = UMAP_pbmc, x = "UMAP1", y = "UMAP2", shape_val = shape_value_pbmc, non_empty_bins = num_non_empty_bins_pbmc)

@@

## To find the benchmark value
benchmark_pbmc <- find_benchmark_value(.data = distance_pbmc, distance_col = distance)
#benchmark_pbmc <- 0.5517801

@@

trimesh_removed_pbmc_umap <- trimesh_removed_pbmc_umap +
  geom_point(size = 0.01, colour = "#33a02c") +
  #ggtitle("(b)") +
  theme_linedraw() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  annotate(geom = 'text', label = 'b', x = -Inf, y = Inf, hjust = -0.5, vjust = 1.5, size = 3)

### 2024-02-01 paper.tex
Add rsults for PBMC with fixed non-empty bins

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, interior hidden, enhanced, frame hidden, breakable, sharp corners]}{\end{tcolorbox}}\fi

@@

\begin{table}[H]
\centering
\begin{tabular}{rrrlr}
  \hline
\textbf{} & \textbf{n\_neighbors} & \textbf{min\_dist} & \textbf{metric} & \textbf{error (x 100) }\\ 
  \hline
\cellcolor{gray!6}{1} & \cellcolor{gray!6}{5.00} & \cellcolor{gray!6}{0.99} & \cellcolor{gray!6}{cosine} & \cellcolor{gray!6}{355.97 }\\ 
  2 & 230.00 & 0.99 & cosine & 378.64 \\ 
\textcolor{red}{\textbf{\cellcolor{gray!6}{  3}}} & \textcolor{red}{\textbf{\cellcolor{gray!6}{30.00}}} & \textcolor{red}{\textbf{\cellcolor{gray!6}{0.30}}} & \textcolor{red}{\textbf{\cellcolor{gray!6}{cosine}}} & \textcolor{red}{\textbf{\cellcolor{gray!6}{386.35 }}}\\ 
   \hline
\end{tabular}
\caption{errors for different parameter combinations} 
\label{tbl-errordiffcomb}
\end{table}

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, interior hidden, boxrule=0pt, frame hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, breakable]}{\end{tcolorbox}}\fi

@@

\begin{table}[H]
\centering
\begin{tabular}{rrrlr}
  \hline
\textbf{} & \textbf{n\_neighbors} & \textbf{min\_dist} & \textbf{metric} & \textbf{error (x 100) }\\ 
  \hline
\cellcolor{gray!6}{1} & \cellcolor{gray!6}{  5} & \cellcolor{gray!6}{0.99} & \cellcolor{gray!6}{cosine} & \cellcolor{gray!6}{262.18 }\\ 
  2 &  15 & 0.99 & cosine & 279.49 \\ 
\cellcolor{gray!6}{  3} & \cellcolor{gray!6}{ 84} & \cellcolor{gray!6}{0.99} & \cellcolor{gray!6}{cosine} & \cellcolor{gray!6}{295.64 }\\ 
  4 &   5 & 0.30 & cosine & 303.90 \\ 
\cellcolor{gray!6}{  5} & \cellcolor{gray!6}{ 15} & \cellcolor{gray!6}{0.30} & \cellcolor{gray!6}{cosine} & \cellcolor{gray!6}{308.97 }\\ 
  6 &  84 & 0.30 & cosine & 319.59 \\ 
\textcolor{red}{\textbf{\cellcolor{gray!6}{  7}}} & \textcolor{red}{\textbf{\cellcolor{gray!6}{ 30}}} & \textcolor{red}{\textbf{\cellcolor{gray!6}{0.30}}} & \textcolor{red}{\textbf{\cellcolor{gray!6}{cosine}}} & \textcolor{red}{\textbf{\cellcolor{gray!6}{386.35 }}}\\ 
   \hline
\end{tabular}
\caption{errors for different parameter combinations} 
\label{tbl-errordiffcomb}
\end{table}
